---
title: "Assignment 2"
author: "Dylan Glave"
date: "4/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DeclareDesign)
library(knitr)

```



Base Theory of Change from Rare: https://www.europarc.org/wp-content/uploads/2015/05/2014-Theory-of-Change-Theory-of-Change.pdf


[]


#### I'll start by exploring code to code out responses for visual underwater surveys. 

- The goal: Understnad the ratio of fishstock biomass inside and outside of a sanctuary no-take zone. 
- Method: Research divers move along two transects (4 sites per transect) inside and outside the sanctuary, twice per year. Once during psawning season for the species, once at six months after spawning
- We'll categorize the possible rations by dividing the "outside" fish biomass (numbers of adults) with "inside" fish. We expect this measurement to between 0 and 1. But the possibility remains of sampling more adult fish outside of the sanctuary. Because of this, I'll leave the possible outputs on a continuos scale with limits of 0 and 2. (Our goal for economic fishery productivity is 0.6, per Rare's oher resources.)




```{r}
# Exploratory code chunk

set.seed(228)

population <- declare_population( #what would go here??
  transect_sites = add_level(N = 8,
            not_scared=sample(c(rep(0,250),rep(1,250)))                
  )
)

pop <- population()

```



Note to Dyl: Ok, that was silly to start with underwater dive surveys. Let's look at..guard logbooks. 



```{r}
set.seed(228)



population_illegal <- declare_population(
  fishers = add_level(N=75, 
     illegal_fishing=sample(c(rep(0,25),rep(1,50))),
     reported=correlate(given = illegal_fishing, rho = 0.5,
                         draw_binary, prob = 0.7)
))

pop_illegal <- population_illegal()

## Using Mark's code, I made the total number of fishers "fishers" N=75
## Then created "illegal_fishing" to represent the total fishers who fish in the sanctuary. ***Not sure how to do this, since I said that each vessel SEEN in the sanctuary is reported, and that would mean the same vessel can be counted twice***
## Last I make "reported" for the proportion that are seen by the enforcement officers.  
```



